Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-18 SupportingInformation.Rmd
log transforming the BMR, not just the mass

<!--checkpoint chunk is moved to makefile.Rmd-->

@@

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/SoilCNraw.pdf}
\includegraphics[width=3 in]{./Results/SoilCNcop.pdf}
\caption[\textbf{(A)} Plot of the raw soil C and N data, \textbf{(B)} Copula plot of soil C and N data]{\textbf{(A)} Plot of the raw soil C and N data, \textbf{(B)} Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n = `r nrow(d)` $ is the number of sampling locations (see \nameref{MT-Model_selection} of manuscript).\label{fig_raw_cop_soilCN}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/BMR_results/rawdataplot_BMR_vs_lnmass.pdf}
\includegraphics[width=3 in]{./Results/BMR_results/copula_BMR_vs_lnmass.pdf}
\caption[\textbf{(A)} Plot of the raw BMR vs. ln(mass) data \textbf{(B)} Copula plot for BMR dataset]{\textbf{(A)} Plot of the raw BMR vs. ln(mass) data \textbf{(B)} Copula plot for BMR dataset. Obtained by applying ranks separately to each variable, and then dividing the ranks by $n+1$ where $n=`r nrow(v_BMR)`$ is the number of contrasts (see \nameref{MT-Model_selection} of manuscript).\label{fig_raw_cop_BMR}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/rawdataplot_AVG_ltoe_humerus.pdf}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/copula_AVG_ltoe_humerus.pdf}
\caption[\textbf{(A)} Plot of the raw AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. \textbf{(B)} Copula plot of AVG.ltoe.IV vs. AVG.humerus phylogenetic traits]{\textbf{(A)} Plot of the raw AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. \textbf{(B)} Copula plot of AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. Obtained by applying ranks separately to each variable, and then dividing the ranks by $n+1$ where $n=`r nrow(v_contrasts_67)`$ is the number of contrasts (see \nameref{MT-Model_selection} of manuscript). \label{fig_raw_cop_AVG_humerus_ltoe}}
\end{center}
\end{figure}

@@

<!--This r-chunk generates figure necessary for maintext Paper-->
```{r fig_stat_testing_for_maintext, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"),mtime("StatTestNumericResults.RData"))}
set.seed(seed) 
source("fig_Paper_stat_testing.R")
#load("./Results/stat_results/stat_testing/StatTestNumericResults.RData")
resultsloc<-"./Results/stat_results/stat_testing/"

copname<-"C"
reslist<-res_pt35_rankT

statname<-"CorlmCoru"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
statname<-"PlmPu"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
statname<-"D2umD2l"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
```

@@

```{r tab_BMR_asym, echo=F, results="markup"}
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
tab_BMR_asym_numbin5<-make_table_stat_fn(data=stat_BMR_ga_numbin5)

knitr::kable(tab_BMR_asym,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis (best fit is here Frank with symmetric tail dep)?, numbin=10 \\label{tab_BMR_asym}",
             booktabs=T)

@@

<!--
## Asymmetric sensitivity and copula structure in populations
           ----moved to Paper.Rmd----
-->

```{r asym_sens_b_variation, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)
#-----------------------------------------------------------------------------------
source("OurBiCopSelect.R")
source("bivfunctionplot.R")
source("asym_sensitivity.R")
#-----------------------------------------------------------------------------------
# This function takes 
# Input :
#       mg : global noise matrix (dim = N by 2)
#       ml : local noise matrix (dim = N by 2)
#       a : a number : local noise coeeficient
#       b : growth factor of pop
#       decrease : logical (controls the nature of global noise)
#       numkeep_last : number of points you want to keep for the pop matrix from the end
#       ploton : logical for optional plot

# Output :
#     a list of 4 pop matrices 
#                         1. (for b=+ve, decrease=F)
#                         2. (for b=+ve, decrease=T)
#                         3. (for b=-ve, decrease=F)
#                         4. (for b=-ve, decrease=T)

plotter_asym_sens_b_varn<-function(mg,ml,a,b,numkeep_last,ploton){

  pop<-Simulator_asym_sens(mg=mg,ml=ml,a=a,b=b,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d<-Simulator_asym_sens(mg=mg,ml=ml,a=a,b=b,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

  neg_b<- -b
  pop_neg_b<-Simulator_asym_sens(mg=mg,ml=ml,a=a,b=neg_b,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d_neg_b<-Simulator_asym_sens(mg=mg,ml=ml,a=a,b=neg_b,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

@@

    #plot(pop[,1],pop[,2],col="red",main = bquote(beta ==.(beta)))
    plot(pop[,1],pop[,2],col="red",xlab=expression(paste(P[1])), ylab=expression(paste(P[2])))
    title(expression(paste("(A) g = ",g[1]," , ")), adj=0.4)
    mtext(paste("b = ",b),side = 3, line=0.2, adj=0.72, col="black")
    plot(pop_d[,1],pop_d[,2],col="blue",xlab=expression(paste(P[1])), ylab=expression(paste(P[2])))
    title(expression(paste("(B) g = ",g[2]," , ")), adj=0.4)
    mtext(paste("b = ",b),side = 3, line=0.2, adj=0.72, col="black")
    plot(pop_neg_b[,1],pop_neg_b[,2],col="orange",xlab=expression(paste(P[1])), ylab=expression(paste(P[2])))
    title(expression(paste("(C) g = ",g[1]," , ")), adj=0.4)
    mtext(paste("b = ",neg_b),side = 3, line=0.2, adj=0.75, col="black")
    plot(pop_d_neg_b[,1],pop_d_neg_b[,2],col="skyblue",xlab=expression(paste(P[1])), ylab=expression(paste(P[2])))
    title(expression(paste("(D) g = ",g[2]," , ")), adj=0.4)
    mtext(paste("b = ",neg_b),side = 3, line=0.2, adj=0.75, col="black")

@@

  return(list(pop=pop,
              pop_d=pop_d,
              pop_neg_b=pop_neg_b,
              pop_d_neg_b=pop_d_neg_b))

}
#----------------------------------------------------------
N<-10000
r<-0.8
a<-0.2
numkeep_last<-1000
temp<-get_noise_glob_loc_mat(N=N,r=r)
mg<-temp$mg
ml<-temp$ml

pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf")
ans_b_0.1<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf")
ans_b_0.9<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=0.9,numkeep_last=numkeep_last,ploton=T)
dev.off()

vlist_b_0.1_b_0.9<-c(ans_b_0.1,ans_b_0.9) # a list of 8 matrices

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AICw","relLTdep_AICw","relUTdep_AICw","p_CvM","p_KS","BS_success%")
#bg <- intToUtf8(0x03B2) 
cnm<-c("b_0.1_g~1~","b_0.1_g~2~","b_-0.1_g~1~","b_-0.1_g~2~","b_0.9_g~1~","b_0.9_g~2~","b_-0.9_g~1~","b_-0.9_g~2~")
#cname<-paste0(bg,cnm)
colnames(summary_stat)<-cnm

ms_asym_b_0.1_b_0.9<-vector(mode = "list", length = 8) # initializing list to store model selection results for all possible b variation
names(ms_asym_b_0.1_b_0.9)<-cnm

stat_npa_asym_b_0.1_b_0.9<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible b variation
names(stat_npa_asym_b_0.1_b_0.9)<-cnm

for(ic in c(1:8)){
  v<-vlist_b_0.1_b_0.9[[ic]]
  res<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=c(1,3:10,13:14,16:20),level=0.05,
                      AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                      gofnormal=F,status=F)

  ms_asym_b_0.1_b_0.9[[ic]]<-res

  summary_stat[1,ic]<-max(res$InfCritRes$AICw)
  summary_stat[2,ic]<-res$InfCritRes$AICw[1]
  summary_stat[3,ic]<-res$relLTdep_AICw
  summary_stat[4,ic]<-res$relUTdep_AICw
  summary_stat[5,ic]<-res$GofRes_CvM
  summary_stat[6,ic]<-res$GofRes_KS
  summary_stat[7,ic]<-(res$Numboot_success/res$Numboot)*100

  stat_npa_asym_b_0.1_b_0.9[[ic]]<-bivfunctionplot(v=v,resloc="./Results/asym_sens_results/",nametag=cnm[ic],numbin=10)

@@

saveRDS(summary_stat,"./Results/asym_sens_results/b_variation_summary_stat.RDS")
saveRDS(ms_asym_b_0.1_b_0.9,"./Results/asym_sens_results/ms_asym_b_0.1_b_0.9.RDS")
saveRDS(stat_npa_asym_b_0.1_b_0.9,"./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
```

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf}
\caption[asym sensitivity results : copula plot]{asym sensitivity results : copula plot \label{fig_ms_asym_b_0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption[asym sensitivity results : copula plot]{asym sensitivity results : copula plot \label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

```{r read_tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")

#for(i in c(1:8)){
#  temp<-make_table_stat_fn(data=tab_asym[[i]])
#  temp2<-knitr::kable(temp, booktabs = T, 
#             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
#      caption =paste(cnm[i]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence."))
#  print(temp2)
#  cat("\\newpage")
#}
```

```{r tab_stat_npa_asym_1,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[1]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[1]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_1}"))
```

\newpage
```{r tab_stat_npa_asym_2,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[2]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[2]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_2}"))
```

\newpage
```{r tab_stat_npa_asym_3,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[3]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[3]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_3}"))
```

```{r tab_stat_npa_asym_4,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[4]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[4]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_4}"))
```

```{r tab_stat_npa_asym_5,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[5]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[5]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_5}"))
```

```{r tab_stat_npa_asym_6,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[6]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[6]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_6}"))
```

```{r tab_stat_npa_asym_7,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[7]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[7]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_7}"))
```

```{r tab_stat_npa_asym_8,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[8]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[8]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_8}"))
```

@@

# References
<div id="refs"></div>

>>>>

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
library(captioner)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```

@@

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/SoilCNraw.pdf}
\includegraphics[width=3 in]{./Results/SoilCNcop.pdf}
\caption[\textbf{(A)} Plot of the raw soil C and N data, \textbf{(B)} Copula plot of soil C and N data]{\textbf{(A)} Plot of the raw soil C and N data, \textbf{(B)} Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n = `r nrow(d)` $ is the number of sampling locations (see Sec. \ref{Model_selection}).\label{fig_raw_cop_soilCN}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/BMR_results/rawdataplot_BMR_vs_lnmass.pdf}
\includegraphics[width=3 in]{./Results/BMR_results/copula_BMR_vs_lnmass.pdf}
\caption[\textbf{(A)} Plot of the raw BMR vs. ln(mass) data \textbf{(B)} Copula plot for BMR dataset]{\textbf{(A)} Plot of the raw BMR vs. ln(mass) data \textbf{(B)} Copula plot for BMR dataset. Obtained by applying ranks separately to each variable, and then dividing the ranks by $n+1$ where $n=`r nrow(v_BMR)`$ is the number of contrasts (see Sec. \ref{Model_selection}).\label{fig_raw_cop_BMR}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/rawdataplot_AVG_ltoe_humerus.pdf}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/copula_AVG_ltoe_humerus.pdf}
\caption[\textbf{(A)} Plot of the raw AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. \textbf{(B)} Copula plot of AVG.ltoe.IV vs. AVG.humerus phylogenetic traits]{\textbf{(A)} Plot of the raw AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. \textbf{(B)} Copula plot of AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. Obtained by applying ranks separately to each variable, and then dividing the ranks by $n+1$ where $n=`r nrow(v_contrasts_67)`$ is the number of contrasts (see Sec. \ref{Model_selection}). \label{fig_raw_cop_AVG_humerus_ltoe}}
\end{center}
\end{figure}

@@

@@

```{r tab_BMR_asym, echo=F, results="markup"}
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
tab_BMR_asym_numbin5<-make_table_stat_fn(data=stat_BMR_ga_numbin5)
knitr::kable(tab_BMR_asym,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis (best fit is here Frank with symmetric tail dep)?, numbin=10 \\label{tab_BMR_asym}",
             booktabs=T)

@@

## Asymmetric sensitivity and copula structure in populations

<!--Another model, distinct from the above, Dan and Shya to discuss-->
```{r asym_sens_beta_variation, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)
source("asym_sensitivity.R")

#-----------------------------------------------------------------------------------
# This function takes 
# Input :
#       N : number of global and local noise points you want
#       rho : covariance of global noise matrix
#       alpha : a number : local noise coeeficient
#       beta : growth factor of pop
#       decrease : logical (controls the nature of global noise)
#       numkeep_last : number of points you want to keep for the pop matrix from the end
#       ploton : logical for optional plot

# Output :
#     a list of 4 pop matrices 
#                         1. (for beta=+ve, decrease=F)
#                         2. (for beta=+ve, decrease=T)
#                         3. (for beta=-ve, decrease=F)
#                         4. (for beta=-ve, decrease=T)

plotter_asym_sens_beta_varn<-function(N,rho,alpha,beta,numkeep_last,ploton){

  pop<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

  neg_beta<- -beta
  pop_neg_beta<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d_neg_beta<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

@@

    plot(pop[,1],pop[,2],col="red",main = bquote(beta ==.(beta)))
    mtext(paste0("(A)"),side = 3, line=0.3, adj=0.3, col="black")
    plot(pop_d[,1],pop_d[,2],col="blue",main = bquote(beta ==.(beta)))
    mtext(paste0("(B)"),side = 3, line=0.3, adj=0.3, col="black")
    plot(pop_neg_beta[,1],pop_neg_beta[,2],col="orange",main = bquote(beta ==.(neg_beta)))
    mtext(paste0("(C)"),side = 3, line=0.3, adj=0.3, col="black")
    plot(pop_d_neg_beta[,1],pop_d_neg_beta[,2],col="skyblue",main = bquote(beta ==.(neg_beta)))
    mtext(paste0("(D)"),side = 3, line=0.3, adj=0.3, col="black")

@@

  return(list(pop=pop,
              pop_d=pop_d,
              pop_neg_beta=pop_neg_beta,
              pop_d_neg_beta=pop_d_neg_beta))

}
#--------------------------------------------------------------
N<-10000
rho<-0.8
alpha<-0.2
numkeep_last<-1000

pdf("./Results/asym_sens_results/beta_0.1_asym_sens.pdf")
ans_beta_0.1<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

pdf("./Results/asym_sens_results/beta_0.9_asym_sens.pdf")
ans_beta_0.9<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.9,numkeep_last=numkeep_last,ploton=T)
dev.off()

vlist_beta_0.1_beta_0.9<-c(ans_beta_0.1,ans_beta_0.9) # a list of 8 matrices

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AIC_w","relLTdep_AICw","relUTdep_AIC_w","p_CvM","p_KS","Numboot_success")
bg <- intToUtf8(0x03B2) 
cnm<-c("_0.1","_0.1_decrease_T","_-0.1","_-0.1_decrease_T","_0.9","_0.9_decrease_T","_-0.9","_-0.9_decrease_T")
cname<-paste0(bg,cnm)
colnames(summary_stat)<-cname

stat_npa_asym_beta_0.1_beta_0.9<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible beta variation
names(stat_npa_asym_beta_0.1_beta_0.9)<-cname

for(ic in c(1:8)){
  v<-vlist_beta_0.1_beta_0.9[[ic]]
  res<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=c(1,3:10,13:14,16:20),level=0.05,
                      AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                      gofnormal=F,status=F)

  summary_stat[1,ic]<-max(res$InfCritRes$AICw)
  summary_stat[2,ic]<-res$InfCritRes$AICw[1]
  summary_stat[3,ic]<-res$relLTdep_AICw
  summary_stat[4,ic]<-res$relUTdep_AICw
  summary_stat[5,ic]<-res$GofRes_CvM
  summary_stat[6,ic]<-res$GofRes_KS
  summary_stat[7,ic]<-res$Numboot_success

  stat_npa_asym_beta_0.1_beta_0.9[[ic]]<-bivfunctionplot(v=v,resloc="./Results/asym_sens_results/",nametag=cname[ic],numbin=10)

@@

saveRDS(summary_stat,"./Results/asym_sens_results/beta_variation_summary_stat.RDS")
saveRDS(stat_npa_asym_beta_0.1_beta_0.9,"./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")
```

![results for model selection \label{fig_ms_asym_beta_0.1}](./Results/asym_sens_results/beta_0.1_asym_sens.pdf){ width=40%, height=40% }

![results for model selection \label{fig_ms_asym_beta_0.9}](./Results/asym_sens_results/beta_0.9_asym_sens.pdf){ width=40%, height=40% }

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
cnm2<-c("b_0.1","b_0.1d_T","b_-0.1","b_-0.1d_T","b_0.9","b_0.9d_T","b_-0.9","b_-0.9d_T")
colnames(summary_stat)<-cnm2
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

\newpage
```{r tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")

for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  temp2<-knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste("beta",cnm[i]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence."))
  print(temp2)
  cat("\\newpage")
}
```

@@

\newpage
# References
<div id="refs"></div>
